---
title: "0. Syllabus Day"
subtitle: "POLI315 International Relations"
author: "Sanghoon Park"
date: "University of South Carolina"
output:
  xaringan::moon_reader:
    lib_dir: libs
    css: ["uofscstyle.css", "uofscfont.css"]
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
      ratio: "16:9"
      self-contained: true
---

```{r setup, include=FALSE}
options(htmltools.dir.version = FALSE)
xaringanExtra::use_panelset()
```


---
class: center, middle
background-image: url("https://github.com/pherephobia/PER_IR_theory_June07/blob/53620c909d2546e70daabdbaf97702d767c97afd/%EA%B5%AD%EC%98%81%EB%AC%B8%ED%98%BC%EC%9A%A9%EC%8B%9C%EA%B7%B8%EB%8B%88%EC%B6%B0_%EA%B0%80%EB%A1%9C_N.gif")
background-size: 300px
background-position: 11% 15%

# Thanks!

## Please do not hesitate to ask questions.

Contacts for Instructor and Teaching Assistant

|                   Contact                                                                          |     Sanghoon Park                                    |   Spencer Baily                            |
| :-----------------------------------------------: | :--------------------------------------------------: | :----------------------------------------: |
| `r icons::fontawesome("paper-plane")`           | [sp23@email.sc.edu](sp23@email.sc.edu)               |  [BAILY@email.sc.edu](BAILY@email.sc.edu)  |
| `r icons::fontawesome("id-card")`                 | [sanghoon-park.com/](https://www.sanghoon-park.com/) |                                            |
| `r icons::fontawesome("building")`                | #305 Gambrell                                        | #303 Gambrell                              |

```{r, echo = F, eval = F, message = F, warning=F, results='hide'}
xaringanBuilder::build_pdf("POLI315-W1-1.html",
                           complex_slides = F, 
                           partial_slides = F)
```

